Legacy Data Confounds Modern Genomics Studies

### 2018-06-19 legacy.tex
small tweaks, fixed biblio

\author[1,2]{Luke Anderson-Trocm\'e}
\author[1,2]{Mathieu Bourgey}
\author[3]{Fumihiko Matsuda}
\author[1,2]{Simon Gravel}

@@

When mismatch sites were removed from the 1kGP data, the  *AC${\rightarrow}$*CC signal disappears \ref{SFS}.
Regressions against different individual-level quality metrics provided by the 1kGP revealed that mean quality per mapped base pair per individual was an excellent correlate with prevalence of the  *AC${\rightarrow}$*CC mutational signature in 1kGP. 
Individuals with low-quality data showing elevated rates of the signature. \ref{PC1_Correlation}
Thus sequences with low mappability harbour mutations that reproduce poorly across studies and exhibit a particular mutational signature.

@@

\begin{center}
 \begin{tabular}{||c c c c c||} 
 \hline
Author & Year & Journal & RSID & PMID \\ [0.5ex] 
 \hline\hline
Comuzzie AG &	2012	 &PLoS One &	rs9469457&23251661\\ 
 \hline
Smith JG &	2012	 & Circ Cardiovasc Genet	& rs7729539&23166209\\ 
 \hline
Ebejer JL	& 2013	 & Twin Res Hum Genet & 	rs6057648&23527680\\ 
 \hline
Zeng Z	& 2014 &	Caries Res	& rs10495332&24556642\\ 
 \hline
Park SL & 	2015	 & PLoS One	& rs113626797&26053186\\ 
 \hline
Parmar PG &	2016	 & Circ Cardiovasc Genet	& rs12370001&26969751\\ 
 \hline
Spada J & 	2016	 & J Sleep Res &	rs12452225&27126917\\ 
 \hline
Astle WJ	& 2016 &	Cell	 & rs533229216&27863252\\ 
 \hline
 Ahola-Olli AV &	2017 &	Am J Hum Genet &	rs76842834&27989323\\ 
 \hline
Liu TC	& 2017 &	JCI Insight &	rs12481514&28352666\\ 
 \hline
  McKay JD & 2017 &	Nature Genetics & 	rs13191445&28604730\\ 
 \hline
Zhou H &	2017	 & JAMA Psychiatry &	rs11179306&	29071344\\ 
 \hline
Tian C	& 2017	 &Nature Communications	 & rs67491322&28928442\\
 \hline
Qian DC	& 2017 &	BMC Genomics &	rs77576211&28927378\\ 
 \hline
Michailidou K	& 2017	 & Nature &	rs76092474&29059683\\ 
 \hline
& & & rs80274284, rs201130852,&\\
Mandage R &	2017	 & PLoS One	 & rs200655768, rs184202621,&28654678\\
& & & rs201255786, rs201761909&\\
 \hline
 \end{tabular}
\end{center}

@@

\bibliography{Legacy.bib}

>>>>

\author[1,2]{Luke Anderson-Trocm\'e}
\author[1,2]{Mathieu Bourgey}
\author[3]{Fumihiko Matsuda (and coauthors)}
\author[1,2]{Simon Gravel}

@@

When mismatch sites were removed from the 1kGP data, the  *AC${\rightarrow}$*CC signal disappears \ref{SFS}.
Regressions against different individual-level quality metrics provided by the 1kGP revealed that mean quality per mapped base pair per individual was an excellent correlate with prevalence of the  *AC${\rightarrow}$*CC mutational signature in 1kGP. 
Individuals with low-quality data showing elevated rates of the signature (see Supplementary Figure \ref{PC1_Correlation}). \sgcomment{fix ref to figs}
Thus sequences with low mappability harbour mutations that reproduce poorly across studies and exhibit a particular mutational signature.

@@

\begin{center}
 \begin{tabular}{l l l r r} 
 \hline
Author & Year & Journal & RSID & PMID \\ [0.5ex] 
 \hline
Comuzzie AG \emph{et al}, PLoS One (2012)  &	2012	 &PLoS One &	rs9469457&23251661\\

Smith JG &	2012	 & Circ Cardiovasc Genet	& rs7729539&23166209\\

Ebejer JL	& 2013	 & Twin Res Hum Genet & 	rs6057648&23527680\\

Zeng Z	& 2014 &	Caries Res	& rs10495332&24556642\\

Park SL & 	2015	 & PLoS One	& rs113626797&26053186\\

Parmar PG &	2016	 & Circ Cardiovasc Genet	& rs12370001&26969751\\

Spada J & 	2016	 & J Sleep Res &	rs12452225&27126917\\ 
Astle WJ	& 2016 &	Cell	 & rs533229216&27863252\\

 Ahola-Olli AV &	2017 &	Am J Hum Genet &	rs76842834&27989323\\

Liu TC	& 2017 &	JCI Insight &	rs12481514&28352666\\

  McKay JD & 2017 &	Nature Genetics & 	rs13191445&28604730\\

Zhou H &	2017	 & JAMA Psychiatry &	rs11179306&	29071344\\

Tian C	& 2017	 &Nature Communications	 & rs67491322&28928442\\

Qian DC	& 2017 &	BMC Genomics &	rs77576211&28927378\\

Michailidou K	& 2017	 & Nature &	rs76092474&29059683\\

& & & rs80274284, rs201130852,&\\
Mandage R &	2017	 & PLoS One	 & rs200655768, rs184202621,&28654678\\
& & & rs201255786, rs201761909&\\
 \hline
 \end{tabular}
\end{center}

@@

\bibliographystyle{plain}
\bibliography{Legacy.bib}
